Nucleosynthesis in a 2M$_{\odot}$ He-Flash Pulse Driven Convection Zone

### 2018-01-25 David Project/Paper/paper_mnras/paper.tex

% Abstract of the paper
\begin{abstract}
During the asymptotic giant branch (AGB) phase of stellar evolution for a 2\Msun, $Z=0.02$ star, the periodic thermal pulses have temperatures as high as 2.9\ee{8} \K. The \neon[22]($\alpha,n$)\magnesium[25] can be activated in these conditions leading to a second activation of the\spr~after it occurring earlier within the \carbon[13] pocket. This adjusts the isotopic per mil ratio of \zirconium[96] and \zirconium[94], $\delta$(\zirconium[96] / \zirconium[94]), due to neutron densities reaching 1\ee{10} \power{\centi\meter}{-3} within the He-flash pulse driven convection zone (PDCZ). With modifications to the diffusion coefficient suggested by 3D hydrodynamic stellar convection simulations, the impact of this to the branching of \zirconium[95] is quantified. These changes to the diffusion coefficient adjust the $\delta$(\zirconium[96] / \zirconium[94]) to better match the observed $\delta$(\zirconium[96] / \zirconium[94]) measured from pre-solar SiC grains.
\end{abstract}

@@

% Kippenhahn figure
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/2M_Kippenhahn.png}
  \caption{Within the He intershell region, the \carbon[13] pocket forms and isotopic ratios are set by the \spr~(\Fig{zr_ratio13C}). It is then mixed and diluted in the He-flash pulse driven convection zone where temperatures get high enough to activate \neon[22]($\alpha,n$)\magnesium[25]. This shifts the isotopic ratios to those shown in \Figure{zr_ratioDil}} 
  \lFig{kipp}
\end{figure}

@@

Another thing to consider is the notion that the only way to know if a numerical result is something that is realistic with the models that were used to compute it, there needs to be numerical convergence. To achieve this, the resolution, or in this case number of time steps, needs to be increased to see if there are changes with the numerical results. If there are very minor changes, the solution that is found can be considered converged. In \Figure{neutron_sub}, the neutron density is measured with two different time steps and are plotted as a function of mass. The neutron density determined with 100 sub-time steps is about six times as large at the mass coordinate of maximum temperature. This shows that the neutron densities were not converged with the zero sub-time steps for the modified diffusion coefficient models. If more time was spent on this work, a few more sub-time steps would have been chosen to check if this 100 sub-time solution is in fact converged.

@@

After running \mppnp~on the \MESA~H5 files with modified diffusion coefficients and 100 sub-time steps, the $\delta$(\zirconium[96] / \zirconium[94]) was calculated throughout the thermal pulse. This is shown in \Figure{zr_results}. Only the last 300 models were calculated due to the computational time needed. They were chosen such that the models with the highest temperatures, where the highest neutron densities would be, were computed. The values of $\delta$(\zirconium[96] / \zirconium[94]) that matter are after the He-flash PDCZ has finished. These are the isotopic ratios that will be drawn to the surface by the third dredge up. In \Figure{zr_results}, the $\delta$(\zirconium[96] / \zirconium[94]) is an average value across the maximum extent of the PDCZ for each model number. The $\delta$(\zirconium[96] / \zirconium[94]) from the zero sub-time steps modified diffusion model produced results that were not expected. The $\delta$(\zirconium[96] / \zirconium[94]) increased meaning that the \zirconium[96] / \zirconium[94] ratio increased while it was expected to decrease due to the supposed smaller neutron densities as discussed in \Sect{neutron}. However, it is likely that this model is not realistic as it may not have been converged as the 100 sub-time step model provided entirely different results. In fact, these results are what had been expected as the number density of \zirconium[96] has decreased from the decrease in neutron density.

>>>>

% Abstract of the paper
\begin{abstract}
During the asymptotic giant branch (AGB) phase of stellar evolution for a 2\Msun, $Z=0.02$ star, the periodic thermal pulses form a \carbon[13] pocket which can start the \spr~from the \carbon[13]($\alpha,n$)\oxygen[16] reaction. Soon after, the He-flash causes a convection zone to form with temperatures as high as 2.9\ee{8} \K~and mixes the contents of the \carbon[13] pocket. With these temperatures, the \neon[22]($\alpha,n$)\magnesium[25] reaction is activated which leads to a second start of the \spr~and this readjusts the isotopic per mil ratio of \zirconium[96] and \zirconium[94], $\delta$(\zirconium[96] / \zirconium[94]), due to neutron densities reaching as high as 1\ee{10} \power{\centi\meter}{-3}. With a modified diffusion coefficient characterized by 3D hydrodynamic stellar convection simulations, the nucleosynthetic impacts at this stage of evolution are described. Of particular interest are the impacts this has for the branching at \zirconium[95] and \iodine[128]. The changes to the diffusion coefficient adjust the $\delta$(\zirconium[96] / \zirconium[94]) to better match the observed $\delta$(\zirconium[96] / \zirconium[94]) measured from pre-solar SiC grains.
\end{abstract}

@@

% Kippenhahn figure
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/2M_Kippenhahn.png}
  \caption{Within the He intershell region, the \carbon[13] pocket forms and isotopic ratios are set by the \spr~(\Fig{zr_ratio13C}). It is then mixed and diluted in the He-flash pulse driven convection zone where temperatures get high enough to activate \neon[22]($\alpha,n$)\magnesium[25]. This shifts the isotopic ratios to those shown in \Figure{zr_ratioDil}.} 
  \lFig{kipp}
\end{figure}

@@

Another thing to consider is the notion that the only way to know if a numerical result is something that is realistic with the models that were used to compute it, there needs to be numerical convergence. To achieve this, the resolution, or in this case number of time steps, needs to be increased to see if there are changes with the numerical results. If there are very minor changes, the solution that is found can be considered converged. In \Figure{neutron_sub}, the neutron density is measured with two different time steps and are plotted as a function of mass. The neutron density determined with 100 sub-time steps is about six times larger than the 0 sub-time step model at the mass coordinate of maximum temperature. This shows that the neutron densities were not converged with the zero sub-time steps for the modified diffusion coefficient models. If more time was spent on this work, a few more sub-time steps would have been chosen to check if this 100 sub-time solution is in fact converged.

@@

After running \mppnp~on the \MESA~H5 files with modified diffusion coefficients and 100 sub-time steps, the $\delta$(\zirconium[96] / \zirconium[94]) was calculated throughout the thermal pulse. This is shown in \Figure{zr_results}. Only the last 300 models were calculated due to the computational time needed. They were chosen such that the models with the highest temperatures, where the highest neutron densities would be, were computed. The values of $\delta$(\zirconium[96] / \zirconium[94]) that matter are after the He-flash PDCZ has finished. These are the isotopic ratios that will be mixed into the H envelope by the third dredge up. In \Figure{zr_results}, the $\delta$(\zirconium[96] / \zirconium[94]) is an average value across the maximum extent of the PDCZ for each model number. The $\delta$(\zirconium[96] / \zirconium[94]) from the zero sub-time steps modified diffusion model produced results that were not expected. However, it is likely that this model is not realistic as it had not been converged as the 100 sub-time step model provided entirely different results. These results are what had been expected as the number density of \zirconium[96] has decreased due to the decrease in neutron density. The $\delta$(\zirconium[96] / \zirconium[94]) from the 100 sub-time steps model is about 40 smaller than the original diffusion coefficient model. This is averaged across the entire PDCZ and so it is a significant difference for when this material gets mixed into the H envelope at the third dredge up. This effect would be amplified by the fact that this will occur for each thermal pulse in this model which there are 25 of.
